---
title: "Week 4: Best practices of deep learning"
# linktitle: "1. Introduction to RStudio and Images"
date: "2025-02-03"
class_date: "2025-02-03"
draft: false
output:
  blogdown::html_page:
    toc: false
menu:
  class:
    parent: Class sessions
    weight: 4
type: docs
weight: 1
# pdf: 
# thumb: 
editor_options: 
  chunk_output_type: console
---

# In-class exercises

Classifying movie reviews, sentiment analysis: a binary classification example, [RMarkdown](../../slides/code/04_Classifying_movie_review_code.Rmd)

Classifying newswires: a multi-class classification example, with questions, [RMarkdown](../../slides/code/04_Classifying_newswires_code.Rmd)

# Working with Keras: A Deep Dive

<a href="../../slides/ch06_DL_Workflow_slides.html#1" target="_blank">Lecture slides in HTML format</a>

```{r echo=FALSE}
knitr::include_url('../../slides/ch06_DL_Workflow_slides.html#1')
```

<a href="../../slides/ch07_Keras_deep_dive_slides.html#1" target="_blank">Lecture slides in HTML format</a>

```{r echo=FALSE}
knitr::include_url('../../slides/ch07_Keras_deep_dive_slides.html#1')
```

Different ways to build Keras models, [RMarkdown](../../slides/code/ch07_2_Keras_models_code.Rmd)

<!-- Training and evaluation loops and metrics, [RMarkdown](../../slides/code/ch07_3_loops_metrics_code.Rmd) -->

