---
title: "Week 5: Convolutional Neural Network"
# linktitle: "1. Introduction to RStudio and Images"
date: "2025-02-10"
class_date: "2025-02-10"
draft: false
output:
  blogdown::html_page:
    toc: false
menu:
  class:
    parent: Class sessions
    weight: 5
type: docs
weight: 1
# pdf: 
# thumb: 
editor_options: 
  chunk_output_type: console
---

### Convolutional Neural Networks

<a href="../../slides/ch08_CNN_slides.html#1" target="_blank">Lecture slides in HTML format</a>

```{r echo=FALSE}
knitr::include_url('../../slides/ch08_CNN_slides.html#1')
```

<a href="../../slides/ch09_CNN_slides.html#1" target="_blank">Lecture slides in HTML format</a>

```{r echo=FALSE}
knitr::include_url('../../slides/ch09_CNN_slides.html#1')
```

<a href="../../slides/ch08_Glossary_slides.html#1" target="_blank">Lecture slides in HTML format</a>

```{r echo=FALSE}
knitr::include_url('../../slides/ch08_Glossary_slides.html#1')
```


### Code

- Introduction to deep learning for computer vision, [RMarkdown, part 1](../../slides/code/ch08_CNN_code1.Rmd), [RMarkdown, part 2](../../slides/code/ch08_CNN_code2.Rmd)

- Image segmentation example, [RMarkdown](../../slides/code/ch09_CNN_code1.Rmd)
- Modern convnet architecture patterns, [RMarkdown](../../slides/code/ch09_CNN_code2.Rmd)
- Interpreting what convnets learn, [RMarkdown](../../slides/code/ch09_CNN_code1.Rmd)


### References

- Computer vision & CNNs: MNIST revisted. by Brad Boehmke. [Slides](https://rstudio-conf-2020.github.io/dl-keras-tf/04-computer-vision-cnns.html#1)

- "How Convolutional Neural Networks work" - 26min video by Brandon Rohrer, https://youtu.be/FmpDIaiMIeA?feature=shared

- [Convolutional Neural Networks (CNNs / ConvNets)](https://cs231n.github.io/convolutional-networks/) - notes from the Stanford CS class CS231n: Convolutional Neural Networks for Visual Recognition. https://cs231n.github.io/

- [Convolution](https://leonardoaraujosantos.gitbook.io/artificial-inteligence/machine_learning/deep_learning/convolution) - detailed review of each operation and layer of a CNN
