---
title: "Section 7: Deep Learning for Text"
# linktitle: "1. Introduction to RStudio and Images"
date: "2025-03-25"
class_date: "2025-03-25"
draft: false
output:
  blogdown::html_page:
    toc: false
menu:
  class:
    parent: Class sessions
    weight: 7
type: docs
weight: 1
# pdf: 
# thumb: 
editor_options: 
  chunk_output_type: console
---

### Deep Learning for Text

<a href="../../slides/ch11a_Text_encoding.html#1" target="_blank">Lecture slides in HTML format</a>

```{r echo=FALSE}
knitr::include_url('../../slides/ch11a_Text_encoding.html#1')
```

<a href="../../slides/ch11b_Text_transformers.html#1" target="_blank">Lecture slides in HTML format</a>

```{r echo=FALSE}
knitr::include_url('../../slides/ch11b_Text_transformers.html#1')
```

### Code

- Text vectorization, embedding, [RMarkdown](../../slides/code/ch11_Text_encoding_code.Rmd)
- Reusing Word2vec embeddings, [RMarkdown](../../slides/code/ch11_Text_word2vec_code.Rmd)
- Attention math demo, [RMarkdown](../../slides/code/ch11_Text_attention_code.Rmd)
- Transformed architecture, [RMarkdown](../../slides/code/ch11_Text_transformers_code.Rmd)
<!-- - Transformer architecture in Keras, [RMarkdown](../../slides/code/ch11_Text_transformers_code.Rmd) -->
<!-- - word2vec demo, [Rmarkdown](../../slides/code/ch11_word2vec.Rmd) -->

<!-- - [Daily Climate time series data](https://www.kaggle.com/datasets/sumanthvrao/daily-climate-time-series-data) -->

<!-- - [Netflix | Stock Market Analysis | Founding Years](https://www.kaggle.com/datasets/whenamancodes/netflix-stock-market-analysis-founding-years) -->

<!-- - [Airbnb, Inc. Stock Market Analysis](https://www.kaggle.com/datasets/whenamancodes/airbnb-inc-stock-market-analysis) -->
<!-- - [META | Stock Market Analysis | Founding Years](https://www.kaggle.com/datasets/whenamancodes/meta-stock-market-analysis-founding-years) -->
<!-- - [TESLA Inc | Stock Market Analysis | Founding Years](https://www.kaggle.com/datasets/whenamancodes/tesla-inc-stock-market-analysis-founding-years) -->
<!-- - [Dogecoin Historical Data](https://www.kaggle.com/datasets/dhruvildave/dogecoin-historical-data) -->

### References

- [Text analysis pipeline](https://text2vec.org/vectorization.html) - text2vec tutorials
- [NLP Illustrated, Part 3: Word2Vec](https://towardsdatascience.com/nlp-illustrated-part-3-word2vec-5b2e12b6a63b/) - word2vec illustrated guide
- Vaswani, Ashish, Noam Shazeer, Niki Parmar, Jakob Uszkoreit, Llion Jones, Aidan N. Gomez, Łukasz Kaiser, and Illia Polosukhin. "Attention is all you need." Advances in neural information processing systems 30 (2017). https://arxiv.org/abs/1706.03762
- [LLMs-from-scratch](https://github.com/rasbt/LLMs-from-scratch) - Implement a ChatGPT-like LLM in PyTorch from scratch, step by step. [Youtube playlist](https://youtube.com/playlist?list=PLTKMiZHVd_2IIEsoJrWACkIxLRdfMlw11)

<!-- - [Understanding LSTM Networks](https://colah.github.io/posts/2015-08-Understanding-LSTMs/) -->