---
title: "Section 8: Generative Deep Learning"
# linktitle: "1. Introduction to RStudio and Images"
date: "2025-04-23"
class_date: "2025-04-23"
draft: false
output:
  blogdown::html_page:
    toc: false
menu:
  class:
    parent: Class sessions
    weight: 8
type: docs
weight: 1
# pdf: 
# thumb: 
editor_options: 
  chunk_output_type: console
---

### Generative Deep Learningcd 

<a href="../../slides/ch12_GAN01_Text_generation.html#1" target="_blank">Lecture slides in HTML format</a>

```{r echo=FALSE}
knitr::include_url('../../slides/ch12_GAN01_Text_generation.html#1')
```

<a href="../../slides/ch12_GAN02_Image_generation.html#1" target="_blank">Lecture slides in HTML format</a>

```{r echo=FALSE}
knitr::include_url('../../slides/ch12_GAN02_Image_generation.html#1')
```

### Code

- Text generation, [RMarkdown](../../slides/code/ch12_GAN01_Text_generation_code.Rmd)
- DeepDream, [RMarkdown](../../slides/code/ch12_GAN02_DeepDream_code.Rmd)
- Style transfer, [RMarkdown](../../slides/code/ch12_GAN03_Style_transfer_code.Rmd)
- Autoencoder, [RMarkdown](../../slides/code/ch12_GAN04_Autoencoder_code.Rmd)
- Generative Adversarial Network, [RMarkdown](../../slides/code/ch12_GAN05_Generative_adversarial_network_code.Rmd)
